\section{Risk metrics}\label{sec:risk}

For each instrument the simulation produces a per-path realised PV
$V_\omega = \sum_k C_\omega(t_k) D(t_k) + V_\omega^T D(T)$. We convert this
to an annualised geometric return $r_\omega = (V_\omega / P_\omega^0)^{1/T}
- 1$ and report a wide risk summary on the empirical distribution of
$\{r_\omega\}_{\omega = 1}^{n_{\text{paths}}}$.

\paragraph{Tail measures.}
\textbf{Value-at-Risk} at confidence $\alpha$ is the empirical quantile
$\VaR_\alpha = -F^{-1}_r(1 - \alpha)$ in sign-positive convention.
\textbf{Expected Shortfall} \autocite{AcerbiTasche2002} is
$\ES_\alpha = -\E[r \given r \le F^{-1}_r(1 - \alpha)]$. We report
$\alpha \in \{0.95, 0.99\}$.

\paragraph{Risk-adjusted ratios.}
The \textbf{Sharpe ratio} is $(\E[r] - r_f) / \sigma(r)$, where $r_f$ is
the empirical mean of the simulated short-rate path; the
\textbf{Sortino ratio} replaces the volatility by the downside-deviation
around $r_f$; the \textbf{Omega ratio} at threshold $\theta$ is the gain-
to-loss density ratio
$\Omega(\theta) = \E[(r - \theta)_+] / \E[(\theta - r)_+]$; the
\textbf{Calmar ratio} divides the mean annual return by the maximum
drawdown of the cumulative cash-flow trajectory.

\paragraph{Tracking error.}
For Model A and Model B we also report tracking error vs the Notaires-INSEE
price-index return, which approximates how closely the realised payoff
follows the broader Paris market.

All metrics are implemented in
\texttt{src/tranche\_pricing/risk/metrics.py} and aggregated via the
\texttt{summary()} helper that drives \cref{tab:headline} below.

\paragraph{Acerbi-Tasche coherence of $\ES_\alpha$.}
A risk measure $\rho$ on a probability space is coherent
\autocite{AcerbiTasche2002} when it satisfies monotonicity, sub-additivity,
positive homogeneity and translation invariance. $\VaR_\alpha$ violates
sub-additivity on non-elliptical distributions — pooling two risky books
can produce a $\VaR$ larger than the sum of their individual $\VaR$s, an
artefact that gave rise to a literature on alternative quantile-based
measures. $\ES_\alpha = -\E[r \mid r \le F^{-1}_r(1-\alpha)]$ resolves
this: Acerbi and Tasche (2002) prove that the integrated tail expectation
\begin{equation*}
\ES_\alpha = -\frac{1}{1 - \alpha}\int_\alpha^1 F^{-1}_r(u)\,\mathrm{d}u
\end{equation*}
is coherent for all $\alpha \in (0, 1)$ on any integrable loss
distribution. We report both: $\VaR_{95}$ for the regulatory
convention, $\ES_{95}$ for the post-2008 view.

\paragraph{Sharpe vs Sortino under a Gaussian return.}
When $r$ is Gaussian with mean $\mu_r$ and volatility $\sigma_r$, the
downside deviation around $r_f$ is
\begin{equation*}
\sigma^-_r = \sqrt{\E[(r_f - r)_+^2]}
            = \sigma_r \sqrt{\Phi(z) + z\,\phi(z) - z^2 \Phi(z)},
\quad z = (r_f - \mu_r)/\sigma_r,
\end{equation*}
so that the Sortino-to-Sharpe ratio is bounded above by $\sqrt 2$ in the
extreme case $r_f \to -\infty$ and converges to $1$ as $r_f \to \mu_r$.
Empirical Sortino divergences from this Gaussian benchmark therefore
quantify the asymmetry of the return distribution, which is why the
equity tranche shows a higher Sortino than Sharpe
(\cref{fig:riskreturn-bars}).

\paragraph{Risk-free benchmark choice.}
Under the \texttt{vasicek\_simulated} discount convention the per-path
mean of $r_t$ is itself stochastic; we use the path-averaged mean
$\bar r = \E\bigl[\frac{1}{N}\sum_k r_{t_k}\bigr]$ as the Sharpe / Sortino
benchmark. Under the \texttt{constant\_at\_initial\_rate} convention the
benchmark collapses to $r_0$ (the spot rate at $t = 0$), reflecting the
"current short rate" interpretation. Both choices are reported in
\texttt{artifacts/results\_meta.json}.

\paragraph{Bootstrap confidence intervals.}
For each instrument the simulation produces a per-path PV vector
$\{V_\omega\}_{\omega = 1}^{n_{\text{paths}}}$. We characterise the
sampling uncertainty of the headline estimator $\bar V$ by a percentile
bootstrap: at each of $B = 1\,000$ resamples we draw $n_{\text{paths}}$
indices with replacement, compute the resample mean
$\bar V^{(b)}$, and report the empirical
$[2.5\,\%, 97.5\,\%]$ quantile of the $\{\bar V^{(b)}\}$ as the
95\,\% confidence interval. The implementation
(\texttt{pricing/tranche\_pricer.py::bootstrap\_fair\_price\_ci}) draws
the resampling matrix in chunks of 200 to bound memory at
$\mathcal{O}(B/200) \times n_{\text{paths}}$ instead of $B \times
n_{\text{paths}}$, and uses a stream-dedicated PCG64 generator so the CIs
are bit-identical across re-runs of the pipeline.
