\clearpage
\appendix
\section{Data sources}\label{app:data}

This appendix documents every external series ingested by
\texttt{tranche-cli data}. Retrieval timestamps and content hashes are
persisted at \texttt{data/raw/\_provenance.json} so the working paper can
be audited against the exact rows used in
\texttt{artifacts/results.csv}.

\paragraph{Notaires de France / INSEE Paris flats price index.}
INSEE BDM series \texttt{010567013}: ``Indice des prix des logements
anciens — Paris — Appartements — Base 100 en moyenne annuelle 2015 — Série
CVS''. Quarterly observations from \dataParisStart{} through
\dataParisEnd{} ($n = \dataParisN{}$). Public access via the BDM SDMX
endpoint \texttt{https://bdm.insee.fr/series/sdmx/data/SERIES\_BDM/010567013}.
We fit GBM and Merton on the quarterly log-returns. Sample notes: the
Paris series was rebased after 2015 (the original 100-base year changed
from 2010), and the post-2020 leg shows the strongest negative
log-returns of the full window — consistent with the recession-shaded
panels of \cref{fig:price-index}.

\paragraph{Indice de Référence des Loyers (INSEE).}
INSEE BDM series \texttt{001515333}, the legal benchmark for residential
rent indexation in France since 2008. Quarterly. We use it only as a
sanity check on the rent-indexation assumption (constant gross yield in
the baseline scenario); no MLE is run on it directly.

\paragraph{French 10Y sovereign yield (OAT 10Y).}
FRED series \texttt{IRLTLT01FRM156N} (``Long-Term Government Bond Yields:
10-year: Main (Including Benchmark) for France''), monthly,
$\dataOatN{}$ observations. Cross-checked against Banque de France
WebStat. Vasicek MLE on the Gaussian transition density yields
$\hat a = \paramVasicekA{}$, $\hat b = \paramVasicekB{}$,
$\hat\sigma_r = \paramVasicekSigma{}$.

\paragraph{ECB AAA euro-area 10Y spot rate.}
Cross-validation only. SDW dataset \texttt{YC}, series key
\texttt{B.U2.EUR.4F.G\_N\_A.SV\_C\_YM.SR\_10Y}. Daily, $\sim$5\,000
observations 2004–2026. The fitted level is materially below the OAT
sample mean — the euro-area AAA basket is dominated by German bunds, so
the levels naturally differ from French sovereign yields.

\paragraph{Case-Shiller US national index.}
FRED \texttt{CSUSHPISA}, monthly. Sole purpose: a sanity check on the GBM
calibration ($\hat\mu, \hat\sigma$ for Paris should not be dramatically
different from a comparable mature market). The Case-Shiller drawdowns of
2007–2011 are far deeper than anything in our Paris sample, which is one
reason the Merton MLE on Paris alone does not identify a jump component
(see \cref{tab:calibration}).

\paragraph{Kenneth French European 3-factor monthly file.}
Tuck-Dartmouth zip distribution. Monthly. We use the risk-free rate (RF)
series only to corroborate the OAT-derived discount rate; the market and
size factors are not consumed by the pricing pipeline.

\paragraph{Visale / ANIL — rental-arrears proxy.}
Visale is the public guarantee operated by Action Logement; ANIL
publishes annual surveys of payment defaults in the private rental
sector. Both ship as PDF tables, not programmatically. We treat the
aggregate annual default rate (around 1.5 – 3 \% over the past decade)
as the prior for $p_d$ in our credit calibration; the copula correlation
$\rho$ is unidentified from a single building and is discussed as a
sensitivity in \cref{sec:results}. The integration of
granular Visale claims data is left as future work.
