\section{Code architecture}\label{app:architecture}

The pipeline is implemented as a flat \texttt{src/tranche\_pricing/}
package, with sub-packages aligned on the conceptual phases of the
working paper. Imports flow strictly downstream: data $\rightarrow$
markets / credit $\rightarrow$ waterfall $\rightarrow$ simulation
$\rightarrow$ pricing $\rightarrow$ viz, mirroring the section ordering of
this paper.

\begin{figure}[h]
\centering
\begin{tikzpicture}[
  node distance=1.1cm and 0.9cm,
  box/.style={rectangle, draw=black!60, rounded corners=2pt, minimum width=2.5cm,
              minimum height=0.7cm, font=\small, align=center, thick},
  data/.style={box, fill=blue!8},
  calib/.style={box, fill=orange!12},
  sim/.style={box, fill=green!10},
  price/.style={box, fill=red!8},
  viz/.style={box, fill=violet!10},
  output/.style={box, fill=black!8, font=\small\ttfamily},
  arrow/.style={-Stealth, thick, black!50},
]
  \node[data] (data) {data};
  \node[calib, right=of data] (calib) {calibration};
  \node[sim, right=of calib] (sim) {simulation};
  \node[price, right=of sim] (price) {pricing};
  \node[viz, right=of price] (viz) {viz};

  \node[box, above=0.4cm of calib, font=\small\ttfamily, fill=blue!4]
       (markets) {markets};
  \node[box, above=0.4cm of sim, font=\small\ttfamily, fill=blue!4]
       (credit) {credit};
  \node[box, above=0.4cm of price, font=\small\ttfamily, fill=blue!4]
       (water) {waterfall};
  \node[box, below=0.4cm of price, font=\small\ttfamily, fill=blue!4]
       (risk) {risk};
  \node[box, below=0.4cm of sim, font=\small\ttfamily, fill=blue!4]
       (insurance) {insurance};

  \node[output, below=1.1cm of viz] (report) {report/};
  \node[output, below=0.3cm of report] (dash) {dashboard/};
  \node[output, above=1.0cm of viz] (csv) {artifacts/*.csv};

  \draw[arrow] (data) -- (calib);
  \draw[arrow] (calib) -- (sim);
  \draw[arrow] (sim) -- (price);
  \draw[arrow] (price) -- (viz);

  \draw[arrow] (markets) -- (calib);
  \draw[arrow] (credit) -- (sim);
  \draw[arrow] (water) -- (price);
  \draw[arrow] (insurance) -- (price);
  \draw[arrow] (risk) -- (price);

  \draw[arrow] (viz) -- (report);
  \draw[arrow] (viz) -- (dash);
  \draw[arrow] (price) |- (csv);
\end{tikzpicture}
\caption{High-level dataflow across the \texttt{src/tranche\_pricing/}
sub-packages. Five primary stages (rounded boxes left-to-right) consume
the supporting modules (lighter boxes top / bottom) and emit the three
artefact families on the right (CSV, LaTeX report, Streamlit dashboard).}
\label{fig:architecture}
\end{figure}

\paragraph{Data flow.}
\begin{enumerate}
  \item \texttt{tranche-cli data} fetches every external series via
        \texttt{data/*.py}, caches it under \texttt{data/.cache/}, and
        writes \texttt{data/raw/*.csv} plus a provenance JSON log.
  \item \texttt{tranche-cli calibrate} runs
        \texttt{calibration/runner.py::run\_all}, which calls the three
        MLEs (GBM closed form, Merton multi-start, Vasicek closed form)
        and serialises everything to
        \texttt{data/processed/calibrated\_params.yaml}.
  \item \texttt{tranche-cli mc} loads the calibrated parameters,
        constructs a \texttt{SimulationConfig} from the active YAML
        scenario, runs \texttt{pricing/model\_compare.compare\_credit\_models}
        for the three credit models, solves fair coupons via
        \texttt{tranche\_pricer.solve\_fair\_coupons\_for\_all}, prices
        the insurance pass with the per-tranche premium allocation, and
        writes \texttt{artifacts/results.csv},
        \texttt{artifacts/fair\_coupons.csv} and
        \texttt{artifacts/results\_meta.json}.
  \item \texttt{report/build\_tables.py} reads those artefacts and
        regenerates the LaTeX tables consumed by every section above.
\end{enumerate}

\paragraph{Configuration discipline.}
Every scenario lives in a YAML under \texttt{config/} validated against
the Pydantic v2 schemas in \texttt{src/tranche\_pricing/config.py}.
Schemas use \texttt{extra="forbid"} so a typo in the YAML fails fast.
The \texttt{extends:} field implements a single level of inheritance with
deep merging, so the stress overlays (\texttt{stress\_gfc.yaml} \emph{et
al.}) need only declare the perturbations.

\paragraph{Variance reduction and reproducibility.}
A single master seed flows through a \texttt{numpy.random.SeedSequence}
that spawns five named sub-streams: \texttt{price, rate, credit, lgd,
qmc}. The engine is bit-identical reproducible across runs (verified in
\texttt{tests/unit/test\_engine.py::test\_engine\_is\_deterministic\_under\_same\_seed}).
Antithetic sampling is applied to every Gaussian draw used in the price,
rate and copula common-factor streams; Sobol QMC (scrambled, scipy
\texttt{qmc.Sobol}) is available as a config switch for the copula
factor.
